A Gentle Introduction to Compressed Sensing

### 2017-01-15 compressed_sensing/cs.tex
cs: modifications

\begin{theorem}
    \label{theorem:CSforRIP}
    Let $\mathbf X_n \in \mathcal M_{n, m} (\mathbb R)$ be $\textrm{RIP}(S, \delta)$ where $S \leq m / 2$ and $\delta \in (0, 1)$. Then for
    $$ n \geqslant C_\delta S \ln(m / S), $$
    where $C_\delta < 1$ is a constant and depends only on $\delta$:
    $$ \hat \beta_n = \beta. $$
\end{theorem}
Proof can be found in Theorem 3.5: \url{mdav.ece.gatech.edu/publications/phdthesis-2010.pdf}.
Let us comment on the result of the theorem.
Suppose, that $S$ is very small comparatively to $m$, then
$$ C_\delta S \ln(m / S) = C_\delta S \ln m - C_\delta S \ln S \approx const \cdot \ln m. $$
It means that we only need to make a number of samples proportional to $\ln m$ instead of $m$ when the assumption about the sparsity is not made.
If $S = m / 2$ then
$$ C_\delta S \ln(m / S) = (C_\delta m \ln 2) / 2 \approx const \cdot m. $$
It means that we need to make a number of samples proportional to $m$.
Consequently, the number of measurements is bounded between $\log m$ and $m$.

@@

\begin{theorem}
    Fix $\delta \in (0, 1)$.
    Let $\mathbf X_n \in \mathcal M_{n, m} (\mathbb R)$ be a random matrix whose components are independent and have $\mathcal N(0, 1/n^2)$ distribution.
    Fix $C_1 > 0$ such as
    $$ n \geqslant C_1 \ln(m / S), $$
    then 
    $$ \mathbb P(\mathbf X_n \in \textrm{RIP}(S, \delta)) \geq 1 - 2 e^{-C_2 n}, $$
    where $C_2 = \delta^2/2C_1 - \ln (42 e / \delta) / C_1$.
\end{theorem}
Proof can be found in Theorem 4.3: \url{mdav.ece.gatech.edu/publications/phdthesis-2010.pdf}.

As we want to make the probability as high as possible, to produce RIP matrix we want $\exp(-C_2n)$ as small as possible.
It means that $C_2 n$ as large as possible.
Let's take $C_1$: $n = C_1 \ln(m / S)$:
$$C_2 n = C_1 C_2 \ln(m / S) = \ln(m / S) [ \delta^2 / 2 - \ln(42 e / \delta) ] = \ln(m/S) [ \delta^2 / 2 + \ln \delta + const ]. $$
So the probability we are interested in depends on $\delta$: the higher $\delta$ is --- the higher the probability is (with fixed $m$).
Consider an extreme example of $\delta = 1$:
$$ \mathbb P(\mathbf X_n \in \textrm{RIP}(S, \delta)) \geq 1 - 2 e^{-C_2 n} = 1 - 2 e^{ \ln{m/S}(0.5 + \ln(42))} \approx 1 - 2 e^{4.2 \ln(m/S)}. $$
WTF???

Let us note that the RIP quality is not the only condition that allows to formulate results similar to the theorem \ref{theorem:CSforRIP}.
There are plenty of them, see Section 3.1.3: \url{https://sites.google.com/site/igorcarron2/cs}.
RIP is somewhat the most traditional.

@@

Let us consider the following elaboration on the optimization problem:
$$ \min_{\beta: \|y_n - \mathbf X_n \beta\|_2^2 \leqslant \delta} \|\beta\|_1 $$
is equivalent to LASSO:
$$ \min_{\beta: \|\beta\|_1 \leqslant t} \|y_n - \mathbf X_n \beta\|_2^2 $$
for a certain $t$.
Thus, we can apply the numerical procedures for LASSO problem (LARS).

\section{Random Fourier projections (Candes et al., 2006)}

@@

\begin{remark}
    The following results about the noisy problem are formulated for RIP matrices and will be out of scope.
\end{remark}

>>>>

\begin{remark}
    \label{rem:def_rip}
    If we (formally) take $\delta_S = 0$ in the Definition \ref{def:rip} we obtain:
    $$ \|\mathbf A x\|_2^2 = \|x\|_2^2 $$
    for all $S$-sparse $x \in \mathbb R^m$.
    It means that the matrix preserves the norm exactly.

    If we take $\delta_S = 1$:
    $$ 0 \leqslant \|\mathbf A x\|_2^2 \leqslant 2 \|x\|_2^2 $$
    for all $S$-sparse $x \in \mathbb R^m$.
    It means that the matrix can diminish the norm infinitely.

    As a result we can interpret the parameter $\delta_S$ like this: the higher $\delta_S$ is --- the higher the dispersion of $\|\mathbf A x\|_2^2$ is.
\end{remark}

\begin{theorem}
    \label{theorem:CSforRIP}
    Let $\mathbf X_n \in \mathcal M_{n, m} (\mathbb R)$ be $\textrm{RIP}(S, \delta)$ where $S \leq m / 2$ and $\delta \in (0, 1)$. Then for
    $$ n \geqslant C_\delta S \ln(m / S), $$
    where $C_\delta < 1$ is a constant and depends only on $\delta$:
    $$ \hat \beta_n = \beta. $$
\end{theorem}

Proof can be found in Theorem 3.5: \url{mdav.ece.gatech.edu/publications/phdthesis-2010.pdf}.
Let us comment on the result of the theorem.
Suppose, that $S$ is very small comparatively to $m$, then
$$ C_\delta S \ln(m / S) = C_\delta S \ln m - C_\delta S \ln S \approx const \cdot \ln m. $$
It means that we only need to make a number of samples proportional to $\ln m$ instead of $m$ when the assumption about the sparsity is not made.
If $S = m / 2$ then
$$ C_\delta S \ln(m / S) = (C_\delta m \ln 2) / 2 \approx const \cdot m. $$
It means that we need to make a number of samples proportional to $m$.
Consequently, the number of measurements is bounded between $\log m$ and $m$.

@@

\begin{theorem}
    Fix $\delta \in (0, 1)$.
    Let $\mathbf X_n \in \mathcal M_{n, m} (\mathbb R)$ be a random matrix whose components are independent and have $\mathcal N(0, 1/n^2)$ distribution.
    Fix $C_1 > 0$ such as
    $$ n \geqslant C_1 \ln(m / S), $$
    then 
    $$ \mathbb P(\mathbf X_n \in \textrm{RIP}(S, \delta)) \geq 1 - 2 e^{-C_2 n}, $$
    where $C_2 = C^*\delta^2/2 - \ln (42 e / \delta) / C_1$ and $C^* = 2 / (1 - \ln(2)) \approx 6.52$.
\end{theorem}
Proof can be found in Theorem 4.3: \url{mdav.ece.gatech.edu/publications/phdthesis-2010.pdf}.

\begin{remark}
    Interested people could analyse the constant $C_2$ to find out its dependence on $\delta$.
    Generally, the higher $n$ is --- the higher the probability is.
\end{remark}

\begin{remark}
    Gaussian matrix is very convenient, as to produce it we only need to transfer random seed but not the matrix itself.
\end{remark}

% As we want to make the probability as high as possible, to produce RIP matrix we want $\exp(-C_2n)$ as small as possible.
% It means that $C_2 n$ as large as possible.
% Let's take $C_1$: $n = C_1 \ln(m / S)$:
% $$C_2 n = C_1 C_2 \ln(m / S) = \ln(m / S) [ \delta^2 / 2 - \ln(42 e / \delta) ] = \ln(m/S) [ \delta^2 / 2 + \ln \delta + const ]. $$
% So the probability we are interested in depends on $\delta$: the higher $\delta$ is --- the higher the probability is (with fixed $m$).
% Consider an extreme example of $\delta = 1$:
% $$ \mathbb P(\mathbf X_n \in \textrm{RIP}(S, \delta)) \geq 1 - 2 e^{-C_2 n} = 1 - 2 e^{ \ln{m/S}(0.5 + \ln(42))} \approx 1 - 2 e^{4.2 \ln(m/S)}. $$
% WTF???

Let us note that the RIProperty  is not the only condition that allows to formulate results similar to the theorem \ref{theorem:CSforRIP}.
There are plenty of them, see Section 3.1.3: \url{https://sites.google.com/site/igorcarron2/cs}.
RIP is somewhat the most traditional.

@@

Let us consider the following elaboration on the optimization problem:
$$ \min_{\beta: \|y_n - \mathbf X_n \beta\|_2^2 \leqslant \delta} \|\beta\|_1 $$
is equivalent to LASSO:
$$ \min_{\beta: \|\beta\|_1 \leqslant t} \|y_n - \mathbf X_n \beta\|_2^2 $$
for a certain $t$.
Thus, we can apply the numerical procedures for LASSO problem (LARS).
\begin{remark}
    When talking about the special features of the algorithm implementation,
    one can mention that the problem is connected to LASSO and, thus, all techniques of convex optimization are applicable here.
\end{remark}

\begin{center}
    \color{red}
    The following sections are optional.
\end{center}
\small {
\section{Random Fourier projections (Candes et al., 2006)}

@@

\begin{remark}
    The following results about the noisy problem are formulated for RIP matrices and will be out of scope.
\end{remark}
}
